---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r message=FALSE, warning=FALSE, paged.print=TRUE, echo=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "85%",
  dpi = 300
)

set.seed(321) # Reproducible results
```

# avlm
Anytime-Valid replacements for base R's lm and aov functions (with additional robust standard error functionality).

[https://arxiv.org/abs/2210.08589](https://arxiv.org/abs/2210.08589).

Contributors:
- Michael Lindon (michael.s.lindon@gmail.com)

# Installation

Install avlm from CRAN:
```r
install.packages("avlm")
```

Or install the development version from GitHub with:
```r
# install.packages("devtools")
devtools::install_github("michaellindon/avlm")
```

# Anytime-Valid Linear Regression

```{r}
library(avlm)

# Generate Data
set.seed(1)
n = 100
X = scale(replicate(3, rnorm(n)), center = TRUE, scale = FALSE)
trt = sample(c(0, 1), size = n, replace = TRUE)
y = 1 + 0*X[,1] + 0*X[,2] + 1.4*X[,3] + 2.3*trt + 2*X[,1]*trt + 3*X[,2]*trt + 0*X[,3]*trt + 1*rnorm(n)
df = data.frame(X)
df$trt = trt
df$y = y

# Tune g to minimize the width of the confidence interval at n
alpha = 0.05
number_of_coefficients = ncol(model.matrix(y ~ . + trt * ., data = df))
g_star = optimal_g(n, number_of_coefficients, alpha)

# Fit a linear model and convert to anytime-valid
classic_fit = lm(y ~ . + trt * ., data = df)
av_fit = av(classic_fit, g = g_star)
```

```{r}
summary(av_fit)
```

```{r}
confint(av_fit)
```

# Robust Anytime-Valid Linear Regression

```{r}
av_fit = av(classic_fit, g=g_star, vcov_estimator = "HC0")
```

```{r}
summary(av_fit)
```

```{r}
confint(av_fit)
```


# Anytime-Valid Anova

```{r}
classic_aov <- aov(Sepal.Length ~ Species, data = iris)
av_aov = av(classic_aov)
```

```{r}
summary(av_aov)
```

# Tidying

We can tidy up the output of both the anytime-valid linear model:
```{r}
tidy(av_fit, conf.int = TRUE)
```

as well as the anytime-valid ANOVA:
```{r}
tidy(av_aov)
```

